Differences from our PPoPP Conference Paper \cite{KBP16}

### 2018-12-14 latex/toms/algorithm.tex
Initial commit for TOMS paper algorithm section

>>>>

\subsection{NLS Algorithms}
This subsection deals with the nonnegative least squares solves needed to update the factor at each inner iteration of the algorithm (\cref{line:locNLS} in \Cref{alg:Par-NNCP-short}). Our framework is capable of supporting any alternating-updating solver~\cite{KBP16}. The NLS solvers which fit this framework and are implemented in our software package are Multiplicative Update~\cite{LS99}, Hierarchical Alternating Least Squares~\cite{CP2009}, Block Principal Pivoting~\cite{KP2011}, Alternating Direction Method of Multipliers~\cite{HSL2016} and Nesterov-type algorithm~\cite{LKLHS2017}. We briefly describe the different solvers below.

\subsubsection{Multiplicative Update (MU)}
\subsubsection{Hierarchical Alternating Least Squares (HALS)}
\subsubsection{Block Principal Pivoting (BPP)}
\subsubsection{Alternating Direction Method of Multipliers (ADMM)}
\subsubsection{Nesterov-type algorithm}
